\LARGE \bf Artificial Cognition for Social Human-Robot Interaction:\\ An Implementation

### 2016-06-20 paper.tex
Update on Overleaf.
Clarify ontology caption following reviewer 2 comment

\address{
$^1$CNRS, LAAS, 7 avenue du Colonel Roche, F-31400 Toulouse, France\\
Univ de Toulouse, LAAS, Toulouse, France\\
{\tt firstname.surname@laas.fr}
}

@@

\caption{The upper part of the {\sc Oro} common-sense TBox. All these concepts
    belong to the {\sc OpenCyc} namespace.}

>>>>

\address{
$^1$LAAS-CNRS, Univ. de Toulouse, CNRS\\
7 avenue du Colonel Roche, F-31400 Toulouse, France\\
{\tt firstname.surname@laas.fr}
}

@@

    \caption{The upper part of the {\sc Oro} common-sense conceptualization
    (TBox). These concepts are shared with the {\sc OpenCyc} upper-ontology.
    They relate to each other through `is-a' subsumption relations.}
